Appendix

### 2020-04-22 appendix/appendixV5.Rmd
testing manual tex

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
output: pdf_document
---

@@

\newpage
```{r, echo=FALSE, fig.width=16, fig.height=16, warning = F,message = FALSE}

#grid.arrange(f1, f2, f3, 
#             f4,f5, f6,
#             f7,
#             ncol = 2,
#             nrow = 4) + rotate()

#grid.arrange(f1,f2) + rotate()
#library(ggplot2)

ggpubr::ggarrange(f1,f2, f3,
                  f4, f5, f6,
                  f7,
#          labels = c("A", "B"),
          ncol = 2, nrow = 4)

#f1 + rotate()

\newpage
```{r, echo=FALSE, fig.width=10, fig.height=10, warning = F,message = FALSE,fig.cap="test size"}

#grid.arrange(f1, f2, f3, 
#             f4,f5, f6,
#             f7,
#             ncol = 2,
#             nrow = 4) + rotate()

#grid.arrange(f1,f2) + rotate()
#library(ggplot2)

ggpubr::ggarrange(f1,f2, f3,
                  f4, f5, f6,
                  f7,
#          labels = c("A", "B"),
          ncol = 3, nrow = 3)  + rotate()

@@

\newpage
### Summary of results
```{r, echo=FALSE, fig.width=17, fig.height=24}

@@

p_1 = image_append(c(plots[[3]], plots[[2]], plots[[1]]), stack = T)
p_2 = image_append(c(plots[[6]], plots[[5]], plots[[4]]), stack = T)
p_3 = image_append(c(plots[[15]],plots[[7]],plots[[15]]), stack = T)
p_full = image_append(c(p_1, p_2, p_3))
p_full

@@

\newpage
```{r, echo=FALSE, fig.width=17, fig.height=24}

print(ggpubr::ggarrange(f8, f9, f11, 
             f10,f12, f13,
             f14,
          ncol = 2,
          nrow = 4)) + rotate()

#ggpubr::ggarrange(f8) + rotate()
#ggpubr::ggarrange(f9) + rotate()

>>>>

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
output:
  pdf_document:
    keep_tex: true
---

@@

```{r, echo=FALSE, fig.width=12.5, fig.height=5}

p_1 = image_append(c(plots[[3]], plots[[2]], plots[[1]]), stack = T)
p_2 = image_append(c(plots[[6]], plots[[5]], plots[[4]]), stack = T)
p_3 = image_append(c(plots[[15]],plots[[7]],plots[[15]]), stack = T)
p_full = image_append(c(p_1, p_2, p_3))

p_full

@@

```{r, echo=FALSE, fig.width=10, fig.height=1}

@@

p_1 = image_append(c(plots[[10]], plots[[9]], plots[[8]]), stack = T)
p_2 = image_append(c(plots[[13]], plots[[12]], plots[[11]]), stack = T)
p_3 = image_append(c(plots[[15]],plots[[14]],plots[[15]]), stack = T)
p_full = image_append(c(p_1, p_2, p_3))

p_full

@@
